\PassOptionsToPackage{pdfpagelabels=false}{hyperref}
\documentclass[10pt,a4paper,sans,colorlinks]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman
\usepackage[utf8]{inputenc}
\usepackage[scale=0.83]{geometry} % Reduce document margins

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{orange} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Luis Enrique} % Your first name
\familyname{Silva Martínez} % Your last name

% All information in this block is optional, comment out any lines you don't need
%\title{Curriculum Vitae}
\address{Don Jaime 114 11, La Santa Cruz}{Santiago de Querétaro, Qro. 76020}
\mobile{951 578 75 48}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{silmar.dll@gmail.com}
%\definecolor{links}{HTML}{2A1B81}
%\hypersetup{urlcolor=links}
\homepage{lesm.github.io/}{https://lesm.github.io} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-2] % Dummy text
%\lipsum[4] % Dummy text

%\makeletterclosing % Print letter signature

\newpage

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title

\section{About me}
  Linux and Vim user, follower of the good development practices like TDD (Test Drive Development), design patterns, code refactoring.
  I like to work with multidisciplinary teams where my colleagues share the use of good development practices, I've experience working with Scrum.
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2011--2018}{Computer Systems Engineering}{Technological Institute of Oaxaca, México}{}{}{}  % Arguments not required can be left empty
%\cventry{2007--2010}{Bachelor of Business Studies}{The University of California}{Berkeley}{\textit{GPA -- 7.5}}{Specialized in Commerce}

%\section{Masters Thesis}

%\cvitem{Title}{\emph{Money Is The Root Of All Evil -- Or Is It?}}
%\cvitem{Supervisors}{Professor James Smith \& Associate Professor Jane Smith}
%\cvitem{Description}{This thesis explored the idea that money has been the cause of untold anguish and suffering in the world. I found that it has, in fact, not.}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvlistdoubleitem{Spanish (Native)}{English, good level.}
%\cvitemwithcomment{English}{Intermediate}{Conversationally fluent (B1 level)}
%\cvitemwithcomment{Dutch}{Basic}{Basic words and phrases only}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Professional Experience}
  \cventry{Aug. 2019 -- Present}{Ruby on Rails Developer}{Zentiglo}{Santiago de Querétaro, Qro}{}{
    Maintaining and upgrading the main Zentiglo's system using TDD, an electronic invoicing system.
    \newline \newline
    Detailed achievements:
    \begin{itemize}
      \item Adding features to the system and the API.
      \item Implementing a module to generate Addendas (CFDI) based on a XSD, using metaprogramming.
      \item Create a script to stamp invoices through the API, using incron to execute the script automatically when a file is uploaded to FTP.
      \item Generation of XSL files for transform XML files.
      \item Updating gems, code refactoring.
      \item Code review
    \end{itemize}
  }
  \cventry{Sept. 2019 -- Dec. 2019}{Ruby on Rails Developer}{Warepow}{Santiago de Querétaro, Qro}{}{
    Adding features into a Ruby on Rails system using TDD, an administrative and financial control system.
  }
  \cventry{Jun. 2018 -- Jul. 2019}{Ruby on Rails Developer}{Freelance}{Oaxaca, México}{}{
    Developing systems with Ruby on Rails using BDD and TDD
    \newline \newline
    Detailed achievements:
    \begin{itemize}
      \item Planning, modeling and coding a system for online sale of books and articles using the Conekta API (payment processing), developed with Rails using TDD.
      \item Planning, modeling and coding a system to report an specific tax to the Mexican Tax Agency (SAT), developed with Rails using BDD y TDD.
    \end{itemize}
  }

  \cventry{May 2016 -- Aug 2018}{Ruby on Rails Developer}{LogicalBricks}{Oaxaca, México}{}{
    Developing for LogicalBricks using TDD and learning from a high performance team.
    \newline \newline
    Detailed achievements:
    \begin{itemize}
      \item Contributing to some private and public LogicalBricks' gems, for example:
        \begin{itemize}
          \item \textbf{fm\_timbrado\_cfdi, fm\_layout and cfdi\_parser}
            \begin{itemize}
              \item Update to support changes of Payroll 1.2 and CFDI 3.3 (Digital tax receipt online)
                following the specifications of SAT (Mexican tax agency) and the PAC Facturación Moderna
                (Provider).
            \end{itemize}
        \end{itemize}
      \item Maintaining and upgrading logicalbricks' main projects, for example.
        \begin{itemize}
          \item \textbf{Infacto (Payroll and Billing)}
            \begin{itemize}
              \item Modeling and coding the new specification Payroll 1.2 and CFDI 3.3 given by the SAT (Mexican tax agency).
              \item In charge of the system adding new features.
            \end{itemize}
          \item \textbf{IDEClara, SinPapel, Prev}
            \begin{itemize}
              \item In charge of the system adding new features.
            \end{itemize}
        \end{itemize}
    \end{itemize}
  }

%----------------------------------------------------------------------------------------
%	Workshops and Conferences
%----------------------------------------------------------------------------------------

\section{Workshops Conferences and Courses}
\subsection{As Attendee}
  \cventry{2014 - 2018}{Talks}{by Ruby Oaxaca community (Oaxaca.rb)}{}{}{
    Action Cable,
    Metaprogramming in ruby,
    Matchers in RSpec,
    APIs in Rails,
    Tmux,
    Vim + Plugins,
    Views in Rails,
    Controllers in Rails,
    Ruby Block, Lambdas and Procs,
    Git,
    TrailBlazer,
    Middleman}
\subsection{As Speaker}
  \cventry{2015}{Workshop}{Introduction to Ruby}{Oaxaca de Juárez, Oaxaca, México}{}{In the XII anniversary of the academic day of Engineering in Computer Systems, organized by Instituto Tecnológico de Oaxaca}
  \cvitem{}{Workshop of 10 hours}
\subsection{As Organizer}
  \cventry{2015-2017}{Workshops}{Coderetreat 2015, 2016 y 2017}{Oaxaca de Juárez, Oaxaca, México}{Global day of CodeRetreat}{}
  \cventry{2015-2018}{Oaxaca.rb}{}{Ruby user community}{}{
    \begin{itemize}
      \item Collaborator in the administration of the community page \href{http://oaxacarb.org/}{Oaxacarb.rb}
      \item Creator of \href{https://oaxacarb.herokuapp.com/}{oaxacarb.herokuapp} to show information about the community's Slack channel.
      \item Responsible for the biweekly campaign of the Coding Dojo, creating the event in EventBrite and sending the invitations through Mailchimp.
    \end{itemize}
}
\subsection{Online Courses}
  \cventry{2015-2018}{}{}{}{}{
    \begin{itemize}
      \item Ruby on Rails: An Introduction - Universidad Johns Hopkins
      \item Rails with Active Record and Action Pack - Universidad Johns Hopkins
      \item HTML, CSS and JavaScript - Universidad Científica y Tecnológica de Hong Kong
    \end{itemize}
  }

%----------------------------------------------------------------------------------------
%\cventry{2011--2012}{Summer Intern}{\textsc{Lehman Brothers}}{Los Angeles}{}{Rated "truly distinctive" for Analytical Skills and Teamwork.}

%------------------------------------------------

%\subsection{Miscellaneous}

%\cventry{2010--2011}{}{}{}{}{Spent some time finding myself. This was a courageous endeavour that didn't have a job title. It was quite important to my overall development though so I'm adding it to my CV. Also it explains the gap in my otherwise stellar CV.}

%\cventry{2009--2010}{Computer Repair Specialist}{Buy More}{Burbank}{}{Worked in the Nerd Herd and helped to solve computer problems. Allowed me to become expert in all forms of martial arts and weaponry.}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

%\section{Awards}

%\cvitem{2011}{School of Business Postgraduate Scholarship}
%\cvitem{2010}{Top Achiever Award -- Commerce}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{General Development Languajes and Tools}
  \cvitem{Languages}{Java, Ruby, SQL, JavaScript}
  \cvitem{Frameworks}{Rails(4,5)  Vue(learning), Bootstrap}
  \cvitem{DBMS}{MySQL, PostgreSQL}
  \cvitem{Linux Systems}{Debian, Ubuntu, ArchLinux, Chakra}
  \cvitem{VCS}{Git(Github, Bitbucket)}
  \cvitem{Continuos Integration}{Semaphore CI, Bitbucket Pipelines}
  \cvitem{Workers}{Delayed\_job, Sidekiq}
  \cvitem{Others}{Vim, Tmux, RVM, Docker, Zsh, Yakuake, Jira, Trello, Redmine}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{RoR Related Development Tools}
  \cvitem{Testing}{Rspect, Minitest, Capybara, Shoulda-Matchers, FactoryGirl/FactoryBot, VCR, WebMock}
  \cvitem{View}{Simpleform, Haml, JQuery, CoffeScript}
  \cvitem{Despliegue}{Capistrano, Nginx, Unicorn, Apache, Passenger, Digital Ocean, Heroku}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

%\section{Interests}

%\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

%\cvlistdoubleitem{Piano}{Chess}
%\cvlistdoubleitem{Cooking}{Dancing}
%\cvlistitem{Running}

%----------------------------------------------------------------------------------------

\end{document}
